% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Projects}{\faLaptop}

\begin{projects}

\project
{MultiModal Insight Engine (WIP)}{Feb 2025 - Present}
{\website{Github}{https://github.com/apassuello/multimodal\_insight\_engine/}}
{Designed and implemented a full-stack training and evaluation platform for Transformer-based multimodal models.
Developed modules for mixed precision, quantization, and pruning; integrated benchmarking tools to compare performance across optimizations.
Built tokenizers and dataloaders for multilingual datasets; supported joint BPE and custom preprocessing.
Integrated pretrained models (with a unified interface for image-text tasks; implemented custom loss functions and schedulers.
Conducted safety evaluations via red teaming frameworks, adversarial generation, and prompt injection testing.}
{PyTorch, Transformers, NLP, Vision Models, Model Optimization, Tokenization, CLIP, ViT, Mixed Precision, Quantization, Pruning, Red Teaming, BLEU/F1/Accuracy, t-SNE, Config Management, Visualization, Logging, Safety Evaluation}
\newpage
\project
{ASIC-Enabled Medical Device Development}{2021 - 2022}
{\website{ADEPT Neuro SA}{https://adeptneuro.com}}
{Development of hardware-software interfaces for novel deep-brain electrodes with integrated ASICs, demonstrating embedded hardware design expertise and complex system integration. Implementation of machine learning-based seizure detection system, achieving excellent academic recognition (5.0/6.0). Project focused on deeply integrated, high-performance medical device platforms within startup environment.}
{Hardware-Software Integration, ASIC Integration, Machine Learning, Medical Devices, C++, Python}
\project
{Data-Driven Analysis of DeepWeb Marketplace Dynamics}{2019}
{\website{EPFL ADA Course}{https://github.com/ADA-2019/Project}}
{Large-scale data analysis project processing over 1TB of historical marketplace data (2013-2015) to study behavioral economics and regulatory impact. Implemented comprehensive data processing pipeline and statistical analysis to evaluate short-term versus long-term marketplace dynamics. Project received distinguished academic recognition (5.5/6.0).}
{Python, Data Analysis, Big Data Processing, Statistical Analysis, Web Scraping, Pandas}
\newpage
\project
{High-Performance Genomic Processing}{2018}
{\github{HEIG-VD-Genomics/FM-Index-FPGA}}
{Implementation of FM-Index algorithm for genomic sequence matching on Artix-7 FPGA platform with HMC memory integration. Developed complete embedded hardware architecture and comprehensive testing infrastructure, achieving performance metrics surpassing traditional software solutions through optimized hardware-software integration. Project earned exceptional recognition (5.5/6.0).}
{FPGA, Verilog, HMC Memory, Genomics, Hardware Architecture, System Testing}

\end{projects}