% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\vspace*{-5mm}
\sectionTitle{Projects}{\faLaptop}
\begin{projects}
\project
{Enterprise Technical Documentation RAG}{Jan 2025 - Present}
{\website{Github}{https://github.com/apassuello/technical-doc-rag/}| \website{Live Demo}{https://huggingface.co/spaces/apassuello/technical-rag/}}
{Engineered end-to-end RAG pipeline processing technical PDFs with 99.5\% optimal chunk rate through custom TOC-aware parsing and quality filtering.
Designed modular architecture with abstract interfaces enabling pluggable components for document processing, embedding, retrieval, and generation.
Implemented production features including streaming responses, session state management, multi-document indexing, and comprehensive error handling.
Achieved 10x search improvement over manual lookup through hybrid retrieval combining semantic understanding with keyword precision (70/30 weighting).
Deployed Streamlit application supporting real-time Q\&A on technical documentation with source citations and confidence scoring.}
{RAG, Hybrid Retrieval, FAISS, BM25, PyTorch, Llama 3.2, HuggingFace, Streamlit, PDF Processing, NLP, Embeddings, Apple Silicon MPS, Docker, Production ML, Technical Documentation, Modular Architecture, pytest, CI/CD}

\project
{MultiModal Insight Engine}{Feb 2025 - Present}
{\website{Github}{https://github.com/apassuello/multimodal\_insight\_engine/}}
{Designed and implemented a full-stack training and evaluation platform for Transformer-based multimodal models.
Developed modules for mixed precision, quantization, and pruning; integrated benchmarking tools to compare performance across optimizations.
Built tokenizers and dataloaders for multilingual datasets (WMT, Europarl, IWSLT); supported joint BPE and custom preprocessing.
Integrated pretrained models (CLIP, ViT) with a unified interface for image-text tasks; implemented custom loss functions and schedulers.
Conducted safety evaluations via red teaming frameworks, adversarial generation, and prompt injection testing.}
{PyTorch, Transformers, NLP, Vision Models, Model Optimization, Tokenization, CLIP, ViT, Mixed Precision, Quantization, Pruning, Red Teaming, BLEU/F1/Accuracy, t-SNE, Config Management, Visualization, Logging, Safety Evaluation}
\newpage
\project
{ASIC-Enabled Medical Device Development}{2021 - 2022}
{\website{ADEPT Neuro SA}{https://adeptneuro.com}}
{Development of hardware-software interfaces for novel deep-brain electrodes with integrated ASICs. Implementation of machine learning-based seizure detection system, achieving excellent academic recognition (5.0/6.0). Project focused on medical device innovation within a startup environment at EPFL Innovation Park.}
{Hardware-Software Integration, ASIC Integration, Machine Learning, Medical Devices, C/C++, Python}

%\project
%{Power Side-Channel Security Analysis}{2021 - 2022}
%{}
%{Research project investigating hardware security vulnerabilities through power side-channel analysis on Zynq-7000 FPGA platform. Implemented comprehensive proof-of-concept attacks in both bare-metal and Linux environments, demonstrating practical security implications. Project received distinguished academic recognition (5.25/6.0).}
%{FPGA, Zynq-7000, Linux, Bare-metal Programming, Security Analysis, Power Side-Channels}

\project
{Data-Driven Analysis of DeepWeb Marketplace Dynamics}{2019}
{\website{EPFL ADA Course}{https://github.com/ADA-2019/Project}}
{Large-scale data analysis project processing over 1TB of historical marketplace data (2013-2015) to study behavioral economics and regulatory impact. Implemented comprehensive data processing pipeline and statistical analysis to evaluate short-term versus long-term marketplace dynamics. Project received distinguished academic recognition (5.5/6.0).}
{Python, Data Analysis, Big Data Processing, Statistical Analysis, Web Scraping, Pandas}

\project
{PriorityQueue Formal Verification}{2019 - 2020}
{\website{}{https://github.com/fquellec/PriorityQueue-FormalVerification}}
{An attempt at proving the correctness of a Stainless implementation of theOptimal Purely Functional Priority Queues introduced by Chris Okasaki and Gerth Stølting Brodal (6.0/6.0)}
{Scala, Stainless, Formal Verification}

%\project
%{High-Performance Genomic Processing}{2018}
%{\github{HEIG-VD-Genomics/FM-Index-FPGA}}
%{Implementation of the FM-Index algorithm for genomic sequence matching on Artix-7 FPGA platform with HMC memory integration. Developed complete hardware architecture and testing infrastructure, achieving performance metrics surpassing traditional software solutions. Project earned exceptional recognition (5.5/6.0).}
%{FPGA, Verilog, HMC Memory, Genomics, Hardware Architecture, System Testing}

\end{projects}