\vspace*{-3mm}\par{%
\iftoggle{firmware}{%
  Senior Firmware Engineer and Software Architect with proven expertise in designing and delivering complex, deeply integrated embedded platforms from concept to production deployment. Combines advanced firmware development experience with cross-functional technical leadership across geographically distributed teams using Agile methodologies, spanning real-time systems, hardware-software integration, and emerging AI-enabled embedded applications. Demonstrated ability to translate product roadmaps into actionable technology strategies while maintaining exceptional quality standards in fast-paced, multiple-project environments.
}{}%
\iftoggle{ai}{%
  \iftoggle{consulting}{%
    Senior Embedded Systems Engineer with proven expertise in safety-critical system development and solid foundation in AI/ML implementation. Combines EPFL Data Science specialization with hands-on experience developing transformer-based multimodal models and LLM-integrated applications. Successfully delivered technical AI/ML education to 100+ international business leaders. Currently building multimodal AI systems and developing LLM-based service architectures. Brings rigorous engineering methodology and regulatory compliance expertise to ethical development and responsible technology implementation.
  }{%
    Senior Embedded Systems Engineer with proven expertise in safety-critical system development and solid foundation in AI/ML implementation. Combines EPFL Data Science specialization with hands-on experience developing transformer-based multimodal models and LLM-integrated applications. Successfully delivered technical AI/ML education to 100+ international business leaders. Currently building production-ready multimodal AI systems and developing LLM-based service architectures. Brings rigorous engineering methodology and regulatory compliance expertise to ethical AI consulting and responsible technology development.
  }%
}{}%
\iftoggle{executive}{%
  Senior Technical Leader with proven expertise in architecting and delivering complex embedded platforms from concept to production deployment. Combines deep firmware development experience with cross-functional technical leadership, spanning real-time systems, hardware-software integration, and emerging AI-enabled embedded applications. Demonstrated ability to drive innovation in resource-constrained environments while maintaining exceptional quality standards. Based in Lausanne with strong collaborative approach to distributed team leadership and technology partner relationships.
}{}%
\iftoggle{general}{%
  Senior Embedded Systems Engineer with proven expertise in safety-critical system development and solid foundation in AI/ML implementation. Combines EPFL Data Science specialization with hands-on experience developing transformer-based multimodal models and LLM-integrated applications. Successfully delivered technical AI/ML education to 100+ international business leaders. Currently building production-ready multimodal AI systems and developing LLM-based service architectures. Brings rigorous engineering methodology and regulatory compliance expertise to ethical AI consulting and responsible technology development.
}{}%
}